### 2011-11-29 docs/src/currydoc.tex

The comments can also contain markups in HTML format
so that special characters like \ccode{<}
must be quoted (e.g., \ccode{\&lt;}).
However, header tags like \code{<h1>} should not be used
since the structuring is generated by CurryDoc.
In addition to Markdown or HTML markups,
one can also mark \emph{references to names} of operations or data types
in Curry programs which are translated into links inside
the generated HTML documentation. Such references have to be
enclosed in single quotes. For instance, the text
\verb!'conc'! refers to the Curry operation \code{conc}
inside the current module whereas the text
\verb!'Prelude.reverse'! refers to the operation \code{reverse}
of the module \code{Prelude}.
If one wants to write single quotes without this specific
meaning, one can escape them with a backslash:
\begin{verbatim}
--- This is a comment without a \'reference\'.
\end{verbatim}
To simplify the writing of documentation comments,
such escaping is only necessary for single words,
i.e., if the text inside quotes has not the syntax of
an identifier, the escaping can be omitted, as in
\begin{verbatim}
--- This isn't a reference.
\end{verbatim}
%
The following example text shows a Curry program with some
documentation comments:
{\renewcommand{\baselinestretch}{1.0}
\begin{verbatim}
--- This is an
--- example module.
--- @author Michael Hanus
--- @version 0.1

@@

--- This data type defines _polymorphic_ trees.
--- @cons Leaf - a leaf of the tree
--- @cons Node - an inner node of the tree
data Tree a = Leaf a | Node [Tree a]
\end{verbatim}
}
\noindent
To generate the documentation, execute the command\pindex{currydoc}
\startprog
currydoc Example
\stopprog
(\code{currydoc} is a command usually stored in \code{$kics2home$/bin}
where $kics2home$ is the installation directory of KiCS2;
see Section~\ref{sec-general}).
This command creates the directory \code{DOC_Example} (if it does not exist)
and puts all HTML documentation files for the main program module
\code{Example}
and all its imported modules in this directory together with
a main index file \code{index.html}.
If one prefers another directory for the documentation files,
one can also execute the command
\startprog
currydoc docdir Example
\stopprog
where \code{docdir} is the directory for the documentation files.

>>>>

The comments can also contain markups in HTML format
so that special characters like \ccode{<}
must be quoted (e.g., \ccode{\&lt;}).
However, header tags like \code{<h1>} should not be used
since the structuring is generated by CurryDoc.
In addition to Markdown or HTML markups,
one can also mark \emph{references to names} of operations or data types
in Curry programs which are translated into links inside
the generated HTML documentation. Such references have to be
enclosed in single quotes. For instance, the text
\verb!'conc'! refers to the Curry operation \code{conc}
inside the current module whereas the text
\verb!'Prelude.reverse'! refers to the operation \code{reverse}
of the module \code{Prelude}.
If one wants to write single quotes without this specific
meaning, one can escape them with a backslash:
\begin{curry}
--- This is a comment without a \'reference\'.
\end{curry}
To simplify the writing of documentation comments,
such escaping is only necessary for single words,
i.e., if the text inside quotes has not the syntax of
an identifier, the escaping can be omitted, as in
\begin{curry}
--- This isn't a reference.
\end{curry}
%
The following example text shows a Curry program with some
documentation comments:
\begin{curry}
--- This is an
--- example module.
--- @author Michael Hanus
--- @version 0.1

@@

--- This data type defines _polymorphic_ trees.
--- @cons Leaf - a leaf of the tree
--- @cons Node - an inner node of the tree
data Tree a = Leaf a | Node [Tree a]
\end{curry}
\noindent
To generate the documentation, execute the command\pindex{currydoc}
\begin{curry}
currydoc Example
\end{curry}
(\code{currydoc} is a command usually stored in \code{$kics2home$/bin}
where $kics2home$ is the installation directory of KiCS2;
see Section~\ref{sec-general}).
This command creates the directory \code{DOC_Example} (if it does not exist)
and puts all HTML documentation files for the main program module
\code{Example}
and all its imported modules in this directory together with
a main index file \code{index.html}.
If one prefers another directory for the documentation files,
one can also execute the command
\begin{curry}
currydoc docdir Example
\end{curry}
where \code{docdir} is the directory for the documentation files.
